Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
update function; add min max; loop for topo variables; close output

# Topographic data
## Data summary 
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

## ANOVAs 
### Elevation
```{r}
mivariable <- 'mde'

# Model 
myformula <- as.formula(paste0(mivariable, " ~ site"))
mymodel <- aov(myformula, data=topo)

auxdf %>% 
  dplyr::filter(variable==mivariable) %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

## Summary model 
tm <- broom::tidy(mymodel)

# See http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1) 
pander(tm, round=5,caption = "ANOVA table", missing = '', 
       emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))

## Multiple comparison 
tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

# Get table 
mymult <- as.data.frame(table_glht(tuk))
pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))
```

### Slope
```{r}
mivariable <- 'slope'

# Model 
myformula <- as.formula(paste0(mivariable, " ~ site"))
mymodel <- aov(myformula, data=topo)

auxdf %>% 
  dplyr::filter(variable==mivariable) %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

## Summary model 
tm <- broom::tidy(mymodel)

# See http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1) 
pander(tm, round=5,caption = "ANOVA table", missing = '', 
       emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))

## Multiple comparison 
tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

# Get table 
mymult <- as.data.frame(table_glht(tuk))
a <- pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))
```

@@

  # Return also summary values 
  summ_values <- df %>% 
    dplyr::select_(mivariable, 'site') %>%
    group_by(site) %>% 
    summarise_each(funs(mean, sd, se=sd(.)/sqrt(n())))

@@

  sink(paste0(di,'out/anovas_competition/aov_', i, '.txt'))
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  sink()
}
```

@@

### Stand Density
```{r}
mivariable <- 'std'
s <- get(paste0('aov_', mivariable))

@@

### Plot Density
```{r}
mivariable <- 'pd'
s <- get(paste0('aov_', mivariable))

@@

### Number of competitors within *r* meters (10 m)
```{r}
mivariable <- 'n_competitors'
s <- get(paste0('aov_', mivariable))

@@

### Number of competitors within *r* meters (10 m) such that $ dbh_j > dbh_i $
```{r}
mivariable <- 'n_competitors_higher'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'sum_sizes'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'sr'
s <- get(paste0('aov_', mivariable))

@@

### Distance to nearest tree       
```{r}
mivariable <- 'dnn'
s <- get(paste0('aov_', mivariable))

@@

### Crowding       
```{r}
mivariable <- 'crowding'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'lorimer'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'nesr'
s <- get(paste0('aov_', mivariable))

@@

### Negative Exponential Weighted size ratio
```{r}
mivariable <- 'newsr'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'srd'
s <- get(paste0('aov_', mivariable))

@@

```{r}
mivariable <- 'sdd'
s <- get(paste0('aov_', mivariable))

@@

>>>>

@@

  # Return also summary values 
  summ_values <- df %>% 
    dplyr::select_(mivariable, 'site') %>%
    group_by(site) %>% 
    summarise_each(funs(mean, sd, se=sd(.)/sqrt(n()), min, max))

@@

  file_out <- file(paste0(di,'out/anovas_competition/aov_', i, '.txt'))
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  sink()
  close(file_out)
}
```

@@

### Stand Density
```{r, echo=FALSE}
mivariable <- 'std'
s <- get(paste0('aov_', mivariable))

@@

### Plot Density
```{r, echo=FALSE}
mivariable <- 'pd'
s <- get(paste0('aov_', mivariable))

@@

### Number of competitors within *r* meters (10 m)
```{r, echo=FALSE}
mivariable <- 'n_competitors'
s <- get(paste0('aov_', mivariable))

@@

### Number of competitors within *r* meters (10 m) such that $ dbh_j > dbh_i $
```{r, echo=FALSE}
mivariable <- 'n_competitors_higher'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'sum_sizes'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'sr'
s <- get(paste0('aov_', mivariable))

@@

### Distance to nearest tree       
```{r, echo=FALSE}
mivariable <- 'dnn'
s <- get(paste0('aov_', mivariable))

@@

### Crowding       
```{r, echo=FALSE}
mivariable <- 'crowding'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'lorimer'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'nesr'
s <- get(paste0('aov_', mivariable))

@@

### Negative Exponential Weighted size ratio
```{r, echo=FALSE}
mivariable <- 'newsr'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'srd'
s <- get(paste0('aov_', mivariable))

@@

```{r, echo=FALSE}
mivariable <- 'sdd'
s <- get(paste0('aov_', mivariable))

@@

# Topographic data

* Read data 
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

* Compare data and export data into text files (see `/out/anovas_topo/`)

```{r, echo=FALSE}
## Comparison 
# Select only variables to compare

topo_sel <- topo %>% dplyr::select(mde, slope, site)

# Get vector with variables 
variables <- c('mde','slope')

  # apply comparison
  out_compara <- compara(df=topo_sel, mivariable = i)

# Loop to export into txt files (see ./out/anovas_topo ... )
for (i in variables){

  file_out <- file(paste0(di,'out/anovas_topo/aov_', i, '.txt'))
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

  sink()
  close(file_out)
}
```

### Elevation

```{r, echo=FALSE}
mivariable <- 'mde'
s <- get(paste0('aov_', mivariable))

### Slope

```{r, echo=FALSE}
mivariable <- 'slope'
s <- get(paste0('aov_', mivariable))

### Min & max mde
